Lesson 4
========================================================

***

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv("pseudo_facebook.tsv", sep = "\t")
qplot(x = age, y = friend_count, data = pf)
```

***

#### What are some things that you notice right away?
Response: youger have more friends

***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) + 
  xlim(13, 90)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_jitter(alpha = 1/20) + 
  xlim(13, 90)
```

#### What do you notice in the plot?
Response:

***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x = age, y = friend_count), data = pf) + 
  geom_point(alpha = 1/20) +
  coord_trans( y = "sqrt") +
  xlim(13, 90)
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x = age, y = friendships_initiated), data = pf) + 
  geom_point(alpha = 1/60) +
  coord_trans( y = "sqrt") +
  xlim(13, 90)
```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
age_groups <- group_by(pf, age)
pf.fc_by_age <- summarise(age_groups,
          friend_count_mean = mean(friend_count),
          friend_count_meadian = median(friend_count),
          n = n())
pf.fc_by_age <- arrange(pf.fc_by_age, age)
```

Create your plot!

```{r Conditional Means Plot}
pf.fc_by_age <- pf %>%
  group_by(age) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age)
head(pf.fc_by_age)
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x = age, y = friend_count), data = pf) +
  xlim(30, 90)+
  geom_point(alpha = 0.05,
             position = position_jitter(h = 0),
             color = 'orange') + 
  coord_trans(y = 'sqrt') + 
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, 
            fun.args = list(probs = .1),
            linetype = 2, color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, 
            fun.args = list(probs = .1),
            color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, 
            fun.args = list(probs = .1),
            linetype = 2, color = 'blue') 
```

#### What are some of your observations of the plot?
Response:
```{r}
ggplot(aes(x = age, y = friend_count), data = pf) +
  coord_cartesian(c(13,90)) +
  geom_point(alpha = 0.05,
             position = position_jitter(h = 0),
             color = 'orange') + 
  geom_line(stat = 'summary', fun.y = mean) +
  geom_line(stat = 'summary', fun.y = quantile, 
            fun.args = list(probs = .1),
            linetype = 2, color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, 
            fun.args = list(probs = .1),
            color = 'blue') +
  geom_line(stat = 'summary', fun.y = quantile, 
            fun.args = list(probs = .1),
            linetype = 2, color = 'blue') 
```

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor(x = pf$age, y = pf$friend_count, use = "all.obs", method = "pearson")
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(       subset(pf, age <= 70)        , cor.test(age, friend_count))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(pf, aes(x=www_likes_received, y=likes_received)) +
  coord_cartesian(xlim = c(0,quantile(pf$www_likes_received, 0.95)),
                  ylim = c(0,quantile(pf$likes_received, 0.95))) +
  geom_point(shape=1) +
  geom_smooth(method = 'lm', color = 'red')
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
with(pf, cor(www_likes_received, likes_received))
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
# install.packages('alr3')
library(alr3)
temp <- data(Mitchell)
temp <- Mitchell
rm(temp)
```

Create your plot!

```{r Temp vs Month}
ggplot(Mitchell, aes(y=Temp, x=Month)) +
  geom_point(shape=1) +
  scale_x_continuous(breaks = seq(0, 203, 12))
with(Mitchell, cor(Month, Temp))
```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
pf$age_with_months <- pf$age + (1 - pf$dob_month / 12)
```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}

```

***

### A New Perspective

What do you notice?
Response:

Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
age_with_months_groups <- group_by(pf, age_with_months)
pf.fc_by_age_months2 <- summarise(age_with_months_groups,
                                  friend_count_mean = mean(friend_count),
                                  friend_count_median =  median(friend_count),
                                  n = n())
pf.fc_by_age_months2 <- arrange(pf.fc_by_age_months2, age_with_months)
                                  
```

***

### Age with Months Means

```{r Age with Months Means}
library(dplyr)
pf.fc_by_age_months <- pf %>%
  group_by(age_with_months) %>%
  summarise(friend_count_mean = mean(friend_count),
            friend_count_median = median(friend_count),
            n = n()) %>%
  arrange(age_with_months)
head(pf.fc_by_age_months)
```

Programming Assignment
```{r Programming Assignment}
ggplot(pf.fc_by_age_months, aes(y=friend_count_mean, x=age_with_months)) +
  geom_point(shape=1)
```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}

```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
ggplot(aes(x = age_with_months, y = friend_count_mean),
       data = subset(pf.fc_by_age_months, age_with_months < 71))+
  geom_line() +
  geom_smooth()
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

